---
title: "Bangladesh COVID-19 Socio-Economic Dashboard"
author: "vasudha"
date: "11/30/2020"
output: html_document
---

Tracking Economic Consequences and Responses to COVID-19 in Bangladesh

Access to information on key economic indicators is essential to help policy-makers in Bangladesh respond to the Covid-19 pandemic.

The dashboard provides data on current economic conditions and trends from administrative and phone based survey in Bangladesh.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#   {.tabset .tabset-pills} 
## Food Security and Market Access {.tabset  .tabset-pills}

### Trends
% hh Skipping Meals

```{r pressure, echo=FALSE}
plot(pressure)
```

% hh able to buy essential food items (compare to previous week)

Amount of rice, lentil, onion and potato bought last time

Share HH facing market closure

Change in commodity prices over time

### Maps

### Definition of Measures

## Income Effect/Seasonality {.tabset  .tabset-pills}

## Exposure to Migration {.tabset  .tabset-pills}

## Social Transfers {.tabset  .tabset-pills}

## COVID-19 Awareness {.tabset  .tabset-pills}

## COVID-19 Symptoms/Health {.tabset  .tabset-pills}

