---
title: "Bangladesh COVID-19 Socio-Economic Dashboard"
author: "Y-RISE & a2i"
date: "Dec 2, 2020"
output: html_document
---

Tracking Economic Consequences and Responses to COVID-19 in Bangladesh

Access to information on key economic indicators is essential to help policy-makers in Bangladesh respond to the Covid-19 pandemic.

The dashboard provides data on current economic conditions and trends from administrative and phone based survey in Bangladesh.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#   Socio-economic indicators {.tabset .tabset-pills} 
## Food Security & Market Access {.tabset  .tabset-pills}

### Trends
% hh Skipping Meals
```{r , echo=FALSE, fig.cap="A caption", out.width = '70%'}
knitr::include_graphics("figures/fd_ins.pdf")
```

```{r pressure, echo=FALSE}
plot(pressure)
```

%hh skipping meals

%hh able to buy essential food items (compare to  previous week)

Amount of rice, lentil, onion and potato bought last time

Share HH facing market closure

Change in commodity prices over time


### Maps

### Definition of Measures

## Income Effect {.tabset  .tabset-pills}

### Trends
Difference in monthly income
(show breakdown by source)


### Maps

### Definition of Measures

## Exposure to Migration {.tabset  .tabset-pills}

### Trends
Food security 

Change in income

% migrate (by district)

% return (by district) – jan-march

YoY Change in Remittance (by district)


### Maps

### Definition of Measures

## Social Transfers {.tabset  .tabset-pills}

### Trends
Number HHs receiving support

Value of the support provided

%hh receiving support from NGO/Govt for Covid-19 


### Maps

### Definition of Measures

## COVID-19 Awareness/Symptoms {.tabset  .tabset-pills}

### Trends
%people wearing mask

%people attend prayers at

%people attend social gatherings

% selling assets to deal with Covid

% people and/or household members experienced any of the symptoms in the past 2 weeks
### Maps

### Definition of Measures

